One Year HPC Certification Forum in Retrospective

### 2019-04-17 paper.tex
edited The HPC Certification Forum section

The HPC Certification Forum (HPCCF) has the role of a (virtual) central authority to curate and maintain a certification program.
The program consists of the definition of competencies, the creation of certificates, and the examination of practitioners to attest that they possess certain competencies.
Moreover, the forum supports tools and an ecosystem around the competencies.

The HPCCF aims to support existing activities and complements them by providing a unified and clear way of mapping out the relevant HPC competencies for practitioners.
Thus, the HPCCF does not regulate the content of training material; we purposely separate the definition of skills and certificates with their examinations from content delivery.
Similarly, the program does not prescribe a curriculum or any fixed order by which skills need to be obtained.

The forum is organized using a Webpage\footnote{http://hpc-certification.org} and utilizes Slack\kh{Vorschlag: kurzen Hinweis zu Slack ergänzen "...  cloud-based set of proprietary team collaboration tools ..." bzw. Link auf die Website} for communication and monthly meetings.
Members are organized in different roles:
Anyone can become an associate member in the HPCCF free of charge -- e.g., observing the status, being listed on the webpage.
Full members must actively contribute to the program to some extent and have voting rights for the roles of the steering board.
The steering board directs the overall activities and is organized in different responsibilities, i.e., into topic-specific chairs.

@@

\paragraph{Management}
At ISC-HPC 2018, the first steering board had been elected.
We established communication channels via webpage, email and Slack for regular discussion.
Slack is also used to conduct our monthly open meetings between members and the steering board.
At beginning we used video conferencing tools, but found that the chat provides a more inclusive discussion and the asynchronous nature is more productive.
We also established relations with various stackholders involved in HPC education growing the participation in the forum.
Meeting notes with action items are extracted from Slack and documented using Google Doc\kh{Vorschlag: kurze Info zum Tool bzw. Link (wie bei Slack) ergänzen}.

>>>>

The HPC Certification Forum (HPCCF) has the role of a (virtual) central authority to curate and maintain the proposed certification program.
The program consists of three parts: the tree of defined competencies, the examination of practitioners to prove they posses those skills, and finally the certification demonstrating their knowledge.     
Although, the forum is not involved in development of any training materials or tools, it supports the ecosystem around the competencies.

The HPCCF aims to support existing activities and complements them by providing a unified and clear way of mapping out the relevant HPC competencies.
Thus, the HPCCF does not regulate the content of training material; we purposely separate the definition of skills, the examination and the certification from content delivery.
Similarly, the program does not prescribe a curriculum or any fixed order by which skills need to be obtained. It eases the navigation between different competencies without being overly restrictive.

The forum is organised around a Webpage\footnote{http://hpc-certification.org},  a GitHub repository\footnote{https://github.com/HPC-certification-forum},  and a could-based team collaboration tool (Slack) for communication and monthly meetings.
The membership is divined into three categories: associate, full and steering board.   
Anyone can become an associate member free of charge, allowing a passive involvement -- e.g., observing the status, being listed on the webpage.
Full members must actively contribute to the program and have voting rights for the roles of the steering board.
The steering board directs the overall activities and is organised in different responsibilities, i.e., into topic-specific chairs. At the moment the steering board has 9 members.

@@

\paragraph{Management}
At ISC-HPC 2018, the first steering board had been elected.
We established communication channels via webpage, email and Slack for regular discussion.
Slack is also used to conduct our monthly open meetings between members and the steering board.
At beginning we used video conferencing tools, but found that the chat provides a more inclusive discussion and the asynchronous nature is more productive.
We also established relations with various stakeholders involved in HPC education growing the participation in the forum.
Meeting notes with action items are extracted from Slack and documented using Google Doc\kh{Vorschlag: kurze Info zum Tool bzw. Link (wie bei Slack) ergänzen}.
